---
title: "Interactive slides using World Bank WDI data"
author: "C Hales"
date: "April 2017"
output: ioslides_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library("plotly")
library("WDI")
```

## Introduction

- This is a short presentation of how the WDI app works.  
- The data is sourced from public data provided by the World Bank development indices using the package [WDI](https://github.com/vincentarelbundock/WDI).
- The G20 individual countries were selected for the exercise.
- The date of the presentation is `r format(Sys.time(), "%d %B, %Y")`.


## Usage of the App and links
- The app was developed using shiny.
- Select the country or coutnries to be plotted using the radio buttons on the left.
- On the right, plots are rendered for both the life expectancy and the GDP per capita time series for the countries selected.
- The average life expectancy and average GDP for the selected countries is calculated and reported above each chart.

###Links

- [shiny app hosted on public website](https://c0nan.shinyapps.io/WDIapp/)
- [Git repository of source code](https://github.com/c0nanh/WDIapp)

## Code snippet used for plotly

START = 1990
END = 2014

dat = WDI(indicator=c("SP.DYN.LE00.IN","NY.GDP.PCAP.PP.KD"), 
          country=c("AR","AU","BR","CA","CN","FR","DE","IN","ID",
                    "IT","JP","KR","MX","RU","SA","ZA","TR","GB","US"), 
          start=START, end=END)

names(dat)[4] <- "Life_Expectancy"  
names(dat)[5] <- "GDP_per_capita"

plot_ly(data=dat,  
        x=~year,  
        y=~Life_Expectancy,  
        z=~GDP_per_capita,  
        type="scatter3d",  
        mode="markers",  
        color=factor(dat$country),  
        name="3D")  

## 3D Scatterplot of data

```{r 3Dplot, echo=FALSE, warning=FALSE, error=FALSE}
START = 1990
END = 2014

dat = WDI(indicator=c("SP.DYN.LE00.IN","NY.GDP.PCAP.PP.KD"), 
          country=c("AR","AU","BR","CA","CN","FR","DE","IN","ID",
                    "IT","JP","KR","MX","RU","SA","ZA","TR","GB","US"), 
          start=START, end=END)

names(dat)[4] <- "Life_Expectancy"
names(dat)[5] <- "GDP_per_capita"

plot_ly(data=dat,
        x=~year,
        y=~Life_Expectancy,
        z=~GDP_per_capita,
        type="scatter3d",
        mode="markers",
        color=factor(dat$country),
        name="3D")
```
